Msc Thesis Figures

### 2025-02-19 docs/msc_thesis_figures.Rmd
trigger GA
comment out lines
fix missing

# Results dir + mun and mrc shapefile
# mun <- st_read("../data/mun/munic_SHP_clean.shp", quiet = TRUE)
# mrc <- st_read("../data/raw/vector/mrc_SHP/mrc_polygone.shp",  quiet = TRUE)
# mrc.mont <- mrc %>% filter(MRS_NM_REG=="Montérégie") 
# mrc.mont.reproj <- st_transform(mrc.mont, crs = st_crs(mun))

>>>>

# Results dir + mun and mrc shapefile
mun <- st_read("../data/mun/munic_SHP_clean.shp", quiet = TRUE)
# mrc <- st_read("../data/raw/vector/mrc_SHP/mrc_polygone.shp",  quiet = TRUE)
# mrc.mont <- mrc %>% filter(MRS_NM_REG=="Montérégie") 
# mrc.mont.reproj <- st_transform(mrc.mont, crs = st_crs(mun))
